Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
push
Update Checkpoint3.Rmd
adding google descriptions

@@

```{r}
google_ts<-read.csv("Time_series_Google.csv")

>>>>

|`KungFluInterest`       | Interest index from google searches by state.     |
|                        | Peak search day=100, all other days in set are    |
|                        | based searches on relative to this peak day.      | 
|`ChinaVirusInterest`    | Interest index from google searches by state.     |
|                        | Peak search day=100, all other days in set are    |
|                        | based searches on relative to this peak day.      | 

@@

```{r}
library(plotly)
google_ts<-read.csv("Time_series_Google.csv")
